Bee brain size is positively associated with urban lifestyles but not with positive population trends

### 2022-12-06 Manuscript/Ms.Rmd
analyses update

labels.minor <- c("Low", "", "High")

@@

#Plot
ggplot(long_data, aes(x=Preference, color= Habitat)) +
    geom_histogram(aes(fill= Habitat)) + 
    xlab("Habitat preference") +
    ylab("Frequency") +
    facet_wrap(~ Habitat) +
    scale_colour_viridis_d(end=0.98)+
    scale_fill_viridis_d(end=0.98) +
    theme_bw() +   
    theme(axis.title = element_text(face = "bold"),
    panel.border=element_rect(size=1), 
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 18,hjust = -0.01),
    strip.background = element_rect(fill = NA, colour = NA, size = 0,linetype="solid"))+
    scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.5),
                       labels = paste0(c(0,0.5,1), "\n", labels.minor)) +
    scale_y_continuous(expand = c(0, 0), limits = c(0,60))+
    geom_vline(aes(xintercept = 0.05), colour="black", linetype="dashed") +
    geom_vline(aes(xintercept = 0.95), colour="black", linetype="dashed")

>>>>

labels.minor <- c("Avoidance", "", "Preference")

@@

#Plot
ggplot(long_data, aes(x=Preference, color= Habitat)) +
    geom_histogram(aes(fill= Habitat)) + 
    xlab("Habitat preference") +
    ylab("Frequency") +
    facet_wrap(~ Habitat) +
    scale_colour_viridis_d(end=0.98)+
    scale_fill_viridis_d(end=0.98) +
    theme_bw() +   
    theme(axis.title = element_text(face = "bold"),
    panel.border=element_rect(size=1), 
    legend.position = "none",
    strip.text = element_text(face = "bold", size = 18,hjust = -0.01),
    strip.background = element_rect(fill = NA, colour = NA, size = 0,linetype="solid"))+
    scale_x_continuous(breaks = c(0.2,0.5,0.8),
                       labels = paste0(c(0,0.5,1), "\n", labels.minor)) +
    scale_y_continuous(expand = c(0, 0), limits = c(0,60))+
    geom_vline(aes(xintercept = 0.20), colour="black", linetype="dashed") +
    geom_vline(aes(xintercept = 0.80), colour="black", linetype="dashed")
